Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-08-08 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
updating descriptions of results to be consistent with new figures; filling out some parts in the results and conclusions

	\par\authorcomment1{Maybe intro is a bit lengthy...where to cut it down?}

@@

	In active region (AR) cores such as those we discuss in this paper, one strategy for constraining potential heating models is the analysis of the emission measure distribution as a function of temperature, $\mathrm{EM}(T)=\int n^2\mathrm{d}h$. \citet{cargill_implications_1994,cargill_nanoflare_2004} predicted that $\mathrm{EM}(T)$ resulting from nanoflare heating should be wide, with a maximum value at $T=T_m\sim10^{6.5}$ K and have a faint, high-temperature (8-10 MK) component. Below $T_m$, there is a scaling $\mathrm{EM}(T)\sim T^a$ over a temperature range $10^6\lesssim T\lesssim T_m$, a result first discussed by \citet{jordan_structure_1975}. Observations from the \textit{Hinode} spacecraft \citep{kosugi_hinode_2007} have shown that $2\lesssim a\lesssim5$, with $T_m\approx10^{6.5-6.6}$ \citep{warren_constraints_2011,warren_systematic_2012,winebarger_using_2011,tripathi_emission_2011,schmelz_cold_2012,del_zanna_evolution_2015}.

@@

	\par A scaling has been claimed for hot emission with $T>T_m$ such that $\mathrm{EM}\propto T^{-b}$, with $b>0$. This fit is usually done in the range $T_m\lesssim T\lesssim10^{7.2}$. However, measured values of these ``hotward" slopes are poorly constrained due to both the low magnitude of emission and the lack of available spectroscopic data in this temperature range \citep{winebarger_defining_2012}. \citet{warren_systematic_2012}, find $7\lesssim b\lesssim10$, with uncertainties of $\pm2.5-3$, for 15 AR cores though \citet{del_zanna_elemental_2014}, using observations from the Solar Maximum Mission, claim larger values for $b$. It must be noted though that reconstructing $\mathrm{EM}(T)$ from spectroscropic and narrow-band observations is non-trivial, with differrent inversion methods often giving significantly different results \citep{landi_monte_2012,guennou_can_2013,aschwanden_benchmark_2015}.

@@

	\par The use of hydrodynamic loop models, combined with sophisticated forward modeling, is a useful method for assessing a wide variety of heating scenarios. Such models of nanoflare-heated loops have found emission measure slopes consistent with those derived from observations in the temperature range $T<T_m$. For example, while \citet{bradshaw_diagnosing_2012} found that the full range of $a$ could not be accounted for with low-frequency nanoflares, \citet{reep_diagnosing_2013} showed that using a tapered nanoflare train allowed for $0.9\lesssim a\lesssim4.5$. \citet{cargill_active_2014}, using a 0D loop model, investigated a large range of heating frequencies, $250<t_N<5000$ s, and found that only when $t_N$ was between a few hundred and 2000 seconds and proportional to the nanoflare energy could the full range of observed emission measure slopes be found. 

@@

	\par However, nanoflare heating requires that we consider a ``train'' of nanoflares along a magnetic strand \citep{viall_patterns_2011,warren_constraints_2011,reep_diagnosing_2013,cargill_modelling_2015}. While a single nanoflare in the LF heating scenario will always occur in a plasma of characteristic AR density ($\sim10^9$ cm$^{-3}$), with significant consequences. In this paper, we use an efficient two-fluid hydrodynamic model to explore the effect of a nanoflare train with varying $t_N$ on $\mathrm{EM}(T)$, in particular for $T>T_m$. Preferential species heating, NEI, power-law nanoflare distributions, and the effects of a variable $t_N$ between events are considered and an emission measure ratio metric, similar to that discussed in \citet{brosius_pervasive_2014}, is used to characterize the various results. \autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated. \autoref{sec:results} shows the resulting emission measure distributions and diagnostics for the entire parameter space. In \autoref{sec:discussion}, we discuss the impacts of two-fluid effects, pre-nanoflare density, and NEI on these calculated observables and how they may be interpreted in the context of nanoflare heating. Finally, \autoref{sec:conclusions} provides some concluding comments on our findings.

@@

	\par 1D hydrodynamic models are excellent tools for computing field-aligned quantities in coronal loops. However, because of the small cell sizes needed to resolve the transition region and consequently small timesteps demanded by thermal conduction, the use of such models in large parameter space explorations is made impractical by long computational runtimes \citep{bradshaw_influence_2013}. We use the popular 0D enthalpy-based thermal evolution of loops (EBTEL) model \citep{klimchuk_highly_2008,cargill_enthalpy-based_2012,cargill_enthalpy-based_2012-1,cargill_modelling_2015} in order to efficiently simulate the evolution of a coronal loop over a large parameter space. This model, which has been successfully benchmarked against the 1D hydrodynamic HYDRAD code of \citet{bradshaw_influence_2013}, computes, with very low computational overhead, time-dependent, spatially-averaged loop quantities.

@@

		\frac{d}{dt}\bar{p}_e &= \frac{\gamma - 1}{L}\left\lbrack\psi_{TR} - (\mathcal{R}_{TR} + \mathcal{R}_C)\right\rbrack + \nonumber\\ &k_B\bar{n}\nu_{ei}(\bar{T}_i - \bar{T}_e) + (\gamma - 1)\bar{Q}_e,\label{eq:ebtel2fl_pe}\\
		\frac{d}{dt}\bar{p}_i &= -\frac{\gamma - 1}{L}\psi_{TR} + k_B\bar{n}\nu_{ei}(\bar{T}_e - \bar{T}_i) +\nonumber\\ &(\gamma - 1)\bar{Q}_i,\label{eq:ebtel2fl_pi}\\

@@

	where $c_2=\bar{T}_e/T_{e,a}\approx0.9$, $c_3=T_{e,0}/T_{e,a}\approx0.6$, $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency and $\psi_{TR}$ is a term included to maintain charge and current and neutrality. Additionally, $c_1=\mathcal{R}_{TR}/\mathcal{R}_C$ and its formulation is discussed in \citet{cargill_enthalpy-based_2012} with additional corrections detailed in Appendix 1 of \citetalias{barnes_inference_2016}. These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$. In the cases where we treat the plasma as a single-fluid, we use the original EBTEL model as described in \citet{klimchuk_highly_2008,cargill_enthalpy-based_2012}.

@@

		\caption{\textbf{Top}: Uniform heating amplitudes for $t_N=1000$ s; \textbf{Middle:} Uniform heating amplitudes for $t_N=5000$ s; \textbf{Bottom:} Heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$. The events shown in red have wait times that depend on the previous event energy while the events shown in blue have uniform wait times. The mean wait time in both cases is $t_N=2000$ s.}

@@

	\par Recent observations have suggested that loops in AR cores are maintained at an equilibrium temperature of $T_{m}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}. Using our modified two-fluid EBTEL model, we have estimated the time-averaged volumetric heating rate needed to keep a loop of half-length $L=40$ Mm at $\bar{T}\approx4$ MK as  $H_{eq}\sim3.6\times10^{-3}$. In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored. Thus, to maintain an emission measure peaked about $T_{m}$, for triangular pulses, the individual event heating rates are constrained by 

@@

		\caption{Total Parameter space covered. ``single'' indicates a single-fluid model. $\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $Q\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent. Note that $(3~\alpha~\mathrm{values})\times(2~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 7 different types of heating functions.}

@@

	\par In our first set of results, we compare $\mathrm{EM}(T)$ for three different types of heating functions, across six different heating frequencies. \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} show the emission measure distributions in the single-fluid case, electron heating case, and ion heating case, respectively. Each panel in each figure corresponds to a different waiting time ($t_N$) and includes three different types of heating functions: uniform heating events (red), events chosen from a power-law distribution of index $\alpha=-2.5$ ($\beta=0$ case, blue), and events chosen from a power-law distribution of index $\alpha=-2.5$ where the time between successive events depends on the heating rate of the preceding event ($\beta=1$ case, green). Note that in all three figures, we show the results for only a single power-law index, $\alpha=2.5$. Furthermore, the dashed lines denote the corresponding NEI cases, $\mathrm{EM}(T_{eff})$. The cases shown in \citetalias{barnes_inference_2016} correspond approximately to the red curves in the lower right panels ($t_N=5000$ s) of each of the three figures since the loop is allowed to cool and drain completely before reheating and a single nanoflare energy is used. 

@@

	\par In \autoref{subsec:heating_stats}, we noted that for heating functions using a power-law energy distribution, for each $t_N$, we run the model $N_R$ times. Thus, for each point in our parameter space, we produce $N_R$ $\mathrm{EM}(T)$ curves. In order to present our results compactly, the solid lines in \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} each show the mean $\mathrm{EM}(T)$ over all $N_R$ curves. The shading represents $1\sigma$ from the mean. In this way, we account for the variations that may occur because of a lack/excess of strong heating events due to limited sampling from the distribution.

@@

	\par We look first at $\mathrm{EM}(T)$ for the single-fluid case, \autoref{fig:single_em}. Firstly, as expected from \citet{cargill_active_2014}, as $t_N$ increases, $\mathrm{EM}(T)$ widens, extending to both cooler ($<4$ MK) and hotter ($>4$ MK) temperatures. The extension toward cooler temperatures arises because as $t_N$ increases there is more time between successive heating events so that the loop so that the loops cools to lower temperatures before being reheated. The dependence on $\alpha$ and $\beta$ is similar to that described in \citet{cargill_active_2014}. The uniform (red) and $\beta=0$ (blue) $\mathrm{EM}(T)$ curves evolve similarly as they extend to cooler temperatures with increasing $t_N$ while the $\beta=1$ curves (green) extend to cooler temperatures much more rapidly. For example, at $t_N=1500$ s, both the uniform and $\beta=0$ cases show little to no emission below 2 MK while the $\beta=1$ cases extends to temperatures well below 1 MK \citep{cargill_active_2014}. As in \citetalias{barnes_inference_2016}, the results below $T_m$ are relatively independent of which species is heated.

@@

	\par The behavior of $\mathrm{EM}(T)$ above $T_m$ is more complicated. For small $t_N$, the emission measure distribution falls off sharply on the hot side for a uniform nanoflare train but a power law distribution leads to a broader distribution above $T_m$. This just reflects the different initial temperatures generated with a power-law distribution since $T \simeq H^{2/7}$. As $t_N$ increases, the distribution for uniform heating gradually broadens as the initial temperature rises due to the lower density in which the heating occurs. A similar broadening occurs for the power laws with the $\beta=0$ and $\beta=1$ results showing little difference. Note that the $\beta=0$ curve is barely visible as it overlaps almost completely with the $\beta=1$ curve. Especially interesting in this case are the results with NEI included. For a uniform nanoflare train, NEI plays no role up to $t_N$ = 2500 sec, but above that it restricts the temperatures that can be detected, as shown in \citetalias{barnes_inference_2016}. This hot emission is relocated to cooler temperatures, resulting in a ``bump'' in the emission measure distribution near 10 MK. On the other hand, NEI plays almost no role in the power law distributions, in both the $\beta=1$ and $\beta=0$ cases.

@@

@@

	\par We now examine several observables often used to characterize the emission measure distribution. The most common observable is the emission measure slope $a$ such that $\mathrm{EM}\propto T^a$ for $10^{5.5}\le T\le10^{6.6}$ K. Both observational and modeling studies have found that $2\lesssim a\lesssim5$ \citep[see Table 3 of][]{bradshaw_diagnosing_2012} and in particular, \citet{cargill_active_2014} found that a heating function of the form $t_N\propto\varepsilon$ was needed in order to account for this range of slopes. Additionally, a similar scaling of $\mathrm{EM}\propto T^{-b}$ for $10^{6.6}\le T\le10^{7.0}$ has been claimed though measurements of $b$ have been subject to large uncertainties \citep{warren_systematic_2012}.

@@

	\par\autoref{fig:em_slope_varying_bounds} shows an example of how both $a$ and $b$ can be calculated from the cool and hot sides of $\mathrm{EM}(T)$, respectively. We select a single sample run from our parameter space in which only the electrons are heated by nanoflares from a power-law distribution of $\alpha=-2.5$ and spaced uniformly by an interval of $t_N=5000$ s. We calculate the resulting $\mathrm{EM}(T)$ and fit $\log{\mathrm{EM}}$ to $a\log{T}$ on $\log{T_{c,min}}<\log{T}<\log{T_{c,max}}$ and $-b\log{T}$ on $\log{T_{h,min}}<\log{T}<\log{T_{h,max}}$ using the Levenburg-Marquardt algorithm for least-squares curve fitting as implemented in the SciPy scientific Python package \citep{van_der_walt_numpy_2011}. We fix the lower limit on each interval such that $T_{c,min}=10^{5.7}$ K and $T_{h,min} = 10^{6.7}$  K and vary the upper limits over $10^{6.1}<T_{c,max}<10^{6.5}$ K and $10^{6.8}<T_{h,max}<10^{7.2}$ K. The left panel of \autoref{fig:em_slope_varying_bounds} shows $a$ (blue) and $b$ (red) as a function upper limit of the fit interval, $T_{c,max}$ (bottom axis) and $T_{h,max}$ (top axis), respectively. The shading denotes the uncertainty of the fit. The right panel of \autoref{fig:em_slope_varying_bounds} shows the resulting fit lines superimposed on the emission measure distribution.

@@

	\par Our results here suggest that while $a$ is an adequate parameter for describing the cool side of $\mathrm{EM}(T)$, the functional form $\mathrm{EM}\sim T^{-b}$ does not adequately capture the character of the hot part of $\mathrm{EM}(T)$ over any reasonable temperature range. \citep{antiochos_evaporative_1978} showed analytically that accounting for evaporative cooling and assuming constant pressure gives $b=11/2$, though this value can be as low as $b=5/2$ if a flux limiter is included. However, in \citetalias{barnes_inference_2016}, we showed that in the case of a single 200 s nanoflare that heats only the electrons, the assumption of constant electron pressure during the heating and early conductive cooling phases does not hold. In this way, we should not expect to recover these analytic values from our numerical or observational results. Clearly, we need an alternate metric to assess the amount of hot plasma seen by the emission measure distribution.
	\par\authorcomment1{I think discussing the results of this section in the context of Paper 1 is a good idea. Not sure how well this works...needs something else?}

@@

		\plottwo{figures/ratio_hist_alpha_single_T2.pdf}{figures/ratio_hist_twait_single_T2.pdf}
		\caption{Histograms of emission measure ratios $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$, where $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.3}$ K, for all heating function types and heating frequencies for the single fluid case. In both panels each histogram is normalized such that for each distribution $P(x)$, $\int_{-\infty}^{\infty}\mathrm{d}x~P(x)=1$ and the bin widths are calculated using the Bayesian blocks method of \citep{scargle_studies_2013} as implemented in the astroML Python package for statistical learning in astronomy \citep{vanderplas_introduction_2012}. \textbf{Left:} Emission measure ratios separated by heating function type for all heating frequencies, $250\le t_N\le5000$ s. \textbf{Right:} Emission measure ratios separated by waiting time, $t_N$. For aesthetic purposes, only five values of $t_N$ are shown, $t_N=1000,2000,3000,4000,5000$ s.}

@@

		\plottwo{figures/ratio_hist_alpha_electron_T2.pdf}{figures/ratio_hist_twait_electron_T2.pdf}

@@

		\plottwo{figures/ratio_hist_alpha_ion_T2.pdf}{figures/ratio_hist_twait_ion_T2.pdf}

@@

	\par\citet{brosius_pervasive_2014}, using observations of an active region from the \textit{EUNIS-13} sounding rocket, found that the intensity ratio of Fe XIX (formed at $T\approx10^{6.95}$ K) to Fe XII (formed at $T\approx10^{6.2}$ K) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside, providing possible evidence for impulsive heating. As a proxy for this intensity ratio and an alternative to the hot emission measure slope $b$, we propose using an emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$. Unlike an emission measure slope, a simple emission measure ratio gives information about the emission at only a single ``hot'' temperature relative to a single ``cool'' temperature. We choose $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.3}\approx2\times10^6$ K, the latter slightly higher (closer to $T_{m}\approx4$ MK) than the formation temperature of Fe XII such that the emission measure ratio is less sensitive to variations in the cool emission and thus a more accurate measure of changes in the amount of hot plasma. The ratio of other emission lines could also be used. 

@@

	\begin{enumerate}
	\item \authorcomment2{$>10$ MK present in nanoflare train runs relative to single pulse results from paper I}
	\item \authorcomment2{consistency of results with Cargill (2014) on the cool side; unsuitability of the hot emission measure slope}
	\item \authorcomment2{importance of density preconditioning in departures from IEQ} 
	\item \authorcomment2{emission measure ratio results in light of Brosius et al, 2014}
	\item \authorcomment2{can we say something about possible heating frequencies? likelihood of electron heating over ion heating?}
	\end{enumerate}

>>>>

@@

	In active region (AR) cores such as those we discuss in this paper, one strategy for constraining potential heating models is the analysis of the emission measure distribution as a function of temperature, $\mathrm{EM}(T)=\int n^2\mathrm{d}h$. \citet{cargill_implications_1994,cargill_nanoflare_2004} predicted that $\mathrm{EM}(T)$ resulting from nanoflare heating should be wide, with a maximum value at $T=T_m\sim10^{6.5}$ K and have a faint, high-temperature (8-10 MK) component. Below $T_m$, there is a scaling $\mathrm{EM}(T)\sim T^a$ over a temperature range $10^6\lesssim T\lesssim T_m$, a result first discussed by \citet{jordan_structure_1975}. Observations from instruments onboard the Solar Dynamics Observatory \citep[SDO,][]{pesnell_solar_2012} and \textit{Hinode} spacecraft \citep{kosugi_hinode_2007} have shown that $2\lesssim a\lesssim5$, with $T_m\approx10^{6.5-6.6}$ \citep{warren_constraints_2011,warren_systematic_2012,winebarger_using_2011,tripathi_emission_2011,schmelz_cold_2012,del_zanna_evolution_2015}.

@@

	\par A scaling has been claimed for hot emission with $T>T_m$ such that $\mathrm{EM}\propto T^{-b}$, with $b>0$. This fit is usually done in the range $T_m\lesssim T\lesssim10^{7.2}$. However, measured values of these ``hotward" slopes are poorly constrained due to both the low magnitude of emission and the lack of available spectroscopic data in this temperature range \citep{winebarger_defining_2012}. \citet{warren_systematic_2012} find $7\lesssim b\lesssim10$ with uncertainties of $\pm2.5-3$, for 15 AR cores though \citet{del_zanna_elemental_2014}, using observations from the Solar Maximum Mission, claim larger values for $b$. It must be noted though that reconstructing $\mathrm{EM}(T)$ from spectroscropic and narrow-band observations is non-trivial, with differrent inversion methods often giving significantly different results \citep{landi_monte_2012,guennou_can_2013,aschwanden_benchmark_2015}.

@@

	\par The use of hydrodynamic loop models, combined with sophisticated forward modeling, is a useful method for assessing a wide variety of heating scenarios. Such models of nanoflare-heated loops have found emission measure slopes consistent with those derived from observations in the temperature range $T<T_m$. For example, while \citet{bradshaw_diagnosing_2012} found that the full range of $a$ could not be accounted for with low-frequency nanoflares, \citet{reep_diagnosing_2013} showed that using a tapered nanoflare train allowed for $0.9\lesssim a\lesssim4.5$. \citet{cargill_active_2014}, using a 0D loop model, investigated a large range of heating frequencies, $250\le t_N\le5000$ s, and found that only when $t_N$ was between a few hundred and 2000 seconds and proportional to the nanoflare energy could the full range of observed emission measure slopes be found. 

@@

	\par While a single nanoflare in the LF heating scenario will always occur in a plasma of characteristic AR density ($\sim10^9$ cm$^{-3}$) with significant consequences, nanoflare heating requires that we consider a ``train'' of nanoflares along a magnetic strand \citep{viall_patterns_2011,warren_constraints_2011,reep_diagnosing_2013,cargill_modelling_2015}. In this paper, we use an efficient two-fluid hydrodynamic model to explore the effect of a nanoflare train with varying $t_N$ on $\mathrm{EM}(T)$, in particular for $T>T_m$. Preferential species heating, NEI, power-law nanoflare distributions, and the effects of a variable $t_N$ between events are considered and an emission measure ratio metric, similar to that discussed in \citet{brosius_pervasive_2014}, is used to characterize the various results. \autoref{sec:methods} discusses the numerical model we have used to conduct this study and the parameter space we have investigated. \autoref{sec:results} shows the resulting emission measure distributions and diagnostics for the entire parameter space. In \autoref{sec:discussion}, we discuss the impacts of two-fluid effects, pre-nanoflare density, and NEI on these calculated observables and how they may be interpreted in the context of nanoflare heating. Finally, \autoref{sec:conclusions} provides some concluding comments on our findings.

@@

	\par Hydrodynamic models are excellent tools for computing field-aligned quantities in coronal loops. However, because of the small cell sizes needed to resolve the transition region and consequently small timesteps demanded by thermal conduction, the use of such models in large parameter space explorations is made impractical by long computational runtimes \citep{bradshaw_influence_2013}. We use the popular 0D enthalpy-based thermal evolution of loops (EBTEL) model \citep{klimchuk_highly_2008,cargill_enthalpy-based_2012,cargill_enthalpy-based_2012-1,cargill_modelling_2015} in order to efficiently simulate the evolution of a coronal loop over a large parameter space. This model, which has been successfully benchmarked against the 1D hydrodynamic HYDRAD code of \citet{bradshaw_influence_2013}, computes, with very low computational overhead, time-dependent, spatially-averaged loop quantities.

@@

		\frac{d}{dt}\bar{p}_e &= \frac{\gamma - 1}{L}\left\lbrack\psi_{TR} - (\mathcal{R}_{TR} + \mathcal{R}_C)\right\rbrack + k_B\bar{n}\nu_{ei}(\bar{T}_i - \bar{T}_e) + (\gamma - 1)\bar{Q}_e,\label{eq:ebtel2fl_pe}\\
		\frac{d}{dt}\bar{p}_i &= -\frac{\gamma - 1}{L}\psi_{TR} + k_B\bar{n}\nu_{ei}(\bar{T}_e - \bar{T}_i) + (\gamma - 1)\bar{Q}_i,\label{eq:ebtel2fl_pi}\\

@@

	where $c_2=\bar{T}_e/T_{e,a}\approx0.9$, $c_3=T_{e,0}/T_{e,a}\approx0.6$, $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency, and $\psi_{TR}$ is a term included to maintain charge and current and neutrality. Additionally, $c_1=\mathcal{R}_{TR}/\mathcal{R}_C$ and its formulation is discussed in \citet{cargill_enthalpy-based_2012} with additional corrections detailed in Appendix 1 of \citetalias{barnes_inference_2016}. These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$. In the cases where we treat the plasma as a single-fluid, we use the original EBTEL model as described in \citet{klimchuk_highly_2008,cargill_enthalpy-based_2012}.

@@

		\caption{Examples of four different heating functions: uniform heating amplitudes for $t_N=1000$ s (top), uniform heating amplitudes for $t_N=5000$ s (middle), and heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$ (bottom). In the bottom panel, the events shown in red have waiting times that depend on the previous event energy while the events shown in blue have uniform wait times. The mean wait time in both cases is $t_N=2000$ s.}

@@

	\par Recent observations have suggested that loops in AR cores are maintained at an equilibrium temperature of $T_{m}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}. Using our modified two-fluid EBTEL model, we have estimated the time-averaged volumetric heating rate needed to keep a loop of half-length $L=40$ Mm at $\bar{T}\approx4$ MK as  $H_{eq}\sim3.6\times10^{-3}$. In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored. Thus, to maintain an emission measure peaked about $T_{m}$, for triangular pulses, the individual event heating rates are constrained by,

@@

		\caption{Total Parameter space covered. ``single'' indicates a single-fluid model. $\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $\varepsilon\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent. Note that $(3~\alpha~\mathrm{values})\times(2~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 7 different types of heating functions per heated species.}

@@

	\par In our first set of results, we compare $\mathrm{EM}(T)$ for three different types of heating functions, across a sample of six different heating frequencies. \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} show the emission measure distributions in the single-fluid case, electron heating case, and ion heating case, respectively. Each panel in each figure corresponds to a different waiting time ($t_N$) and includes three different types of heating functions: uniform heating events (red), events chosen from a power-law distribution of index $\alpha=-2.5$ ($\beta=0$ case, blue), and events chosen from a power-law distribution of index $\alpha=-2.5$ where the time between successive events depends on the heating rate of the preceding event ($\beta=1$ case, green). Note that in all three figures, we show the results for only a single power-law index, $\alpha=2.5$. Furthermore, the dashed lines denote the corresponding NEI cases, $\mathrm{EM}(T_{eff})$. The cases shown in \citetalias{barnes_inference_2016} correspond approximately to the red curves in the lower right panels ($t_N=5000$ s) of each of the three figures since the loop is allowed to cool and drain completely before reheating and a single nanoflare energy is used. 

@@

	\par In \autoref{subsec:heating_stats}, we noted that for heating functions using a power-law energy distribution, for each $t_N$, we run the model $N_R$ times. Thus, for each point in our parameter space, we produce $N_R$ $\mathrm{EM}(T)$ curves. In order to present our results compactly, the solid lines in \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} each show the mean $\mathrm{EM}(T)$ over all $N_R$ curves. The shading represents $1\sigma$ from the mean. In this way, we account for the variations that may occur because of a lack/excess of strong heating events due to limited sampling from the power-law distribution of possible heating rates.

@@

	\par We look first at $\mathrm{EM}(T)$ for the single-fluid case, \autoref{fig:single_em}. Firstly, as expected from \citet{cargill_active_2014}, as $t_N$ increases, $\mathrm{EM}(T)$ widens, extending to both cooler ($<4$ MK) and hotter ($>4$ MK) temperatures. The extension toward cooler temperatures arises because as $t_N$ increases there is more time between successive heating events so that the loop cools to lower temperatures before being reheated. The dependence on $\alpha$ and $\beta$ is similar to that described in \citet{cargill_active_2014}. The uniform (red) and $\beta=0$ (blue) $\mathrm{EM}(T)$ curves evolve similarly as they extend to cooler temperatures with increasing $t_N$ while the $\beta=1$ curves (green) extend to cooler temperatures much more rapidly. For example, at $t_N=1500$ s, both the uniform and $\beta=0$ cases show little to no emission below 2 MK while the $\beta=1$ cases extends to temperatures well below 1 MK \citep{cargill_active_2014}. As in \citetalias{barnes_inference_2016}, the results below $T_m$ are relatively independent of which species is heated.

@@

	\par The behavior of $\mathrm{EM}(T)$ above $T_m$ is more complicated. For small $t_N$, the emission measure distribution falls off sharply on the hot side for a uniform nanoflare train but a power-law distribution leads to a broader distribution above $T_m$. This just reflects the different initial temperatures generated with a power-law distribution since $T \simeq H^{2/7}$. As $t_N$ increases, the distribution for uniform heating gradually broadens as the initial temperature rises due to the lower density in which the heating occurs. A similar broadening occurs for the power laws with the $\beta=0$ and $\beta=1$ results showing little difference. Note that the $\beta=0$ curve is barely visible as it overlaps almost completely with the $\beta=1$ curve. Especially interesting in this case are the results with NEI included. For a uniform nanoflare train, NEI plays no role up to $t_N$ = 2500 sec, but above that it restricts the temperatures that can be detected, as shown in \citetalias{barnes_inference_2016}. This hot emission is relocated to cooler temperatures, resulting in a ``bump'' in the emission measure distribution near 10 MK. On the other hand, NEI plays almost no role in the power law distributions, in both the $\beta=1$ and $\beta=0$ cases.

@@

	The relation of these results to potential solar observations is made difficult by incomplete temperature coverage. For example, we noted earlier that the temperature coverage for \textit{Hinode} and SDO is good for $T<T_m$, but patchy for $T>T_m$. On the other hand, the proposed MaGIXS instrument has the opposite performance regime. This differs from EUVE observations of some stellar coronae which have very complete temperature coverage from $10^6$ K to over $10^7$ K \citep[e.g.][]{sanz-forcada_structure_2003}, and have been modeled using low frequency nanoflares \citep{cargill_temperature-emission_2006}. In the following sub-sections we propose ways that the paucity of solar temperature coverage can be partially remedied.

@@

	\par As we discussed in the \autoref{sec:intro}, a commonly-used observable is the emission measure slope $a$ such that $\mathrm{EM}\propto T^a$ for $10^{5.5}\le T\le10^{6.6}$ K. Both observational and modeling studies have found that $2\lesssim a\lesssim5$ \citep[see Table 3 of][]{bradshaw_diagnosing_2012} and in particular, \citet{cargill_active_2014} found that a heating function of the form $t_N\propto\varepsilon$ was needed in order to account for this range of slopes. The EIS instrument \citep{culhane_euv_2007} on \textit{Hinode} permits good temperature coverage. Additionally, a similar scaling of $\mathrm{EM}\propto T^{-b}$ for $10^{6.6}\le T\le10^{7.0}$ has been claimed though measurements of $b$ have been subject to large uncertainties \citep{warren_systematic_2012} due to intermittent temperature coverage.

@@

	\par\autoref{fig:em_slope_varying_bounds} shows an example of how both $a$ and $b$ can be calculated from the cool and hot sides of $\mathrm{EM}(T)$, respectively. We select a single sample run from our parameter space in which only the electrons are heated by nanoflares from a power-law distribution of $\alpha=-2.5$ and spaced uniformly by an interval of $t_N=5000$ s. We calculate the resulting $\mathrm{EM}(T)$ and fit $\log{\mathrm{EM}}$ to $a\log{T}$ on $\log{T_{c,min}}<\log{T}<\log{T_{c,max}}$ and $-b\log{T}$ on $\log{T_{h,min}}<\log{T}<\log{T_{h,max}}$ using the Levenburg-Marquardt algorithm for least-squares curve fitting as implemented in the scipy scientific Python package \citep{van_der_walt_numpy_2011}. We fix the lower limit on each interval such that $T_{c,min}=10^{5.7}$ K and $T_{h,min} = 10^{6.7}$  K and vary the upper limits over $10^{6.1}<T_{c,max}<10^{6.5}$ K and $10^{6.8}<T_{h,max}<10^{7.2}$ K. The left panel of \autoref{fig:em_slope_varying_bounds} shows $a$ (blue) and $b$ (red) as a function upper limit of the fit interval, $T_{c,max}$ (bottom axis) and $T_{h,max}$ (top axis), respectively. The shading denotes the uncertainty of the fit. The right panel of \autoref{fig:em_slope_varying_bounds} shows the resulting fit lines superimposed on the emission measure distribution.

@@

	\par Our results here suggest that while $a$ is an adequate parameter for describing the cool side of $\mathrm{EM}(T)$, the functional form $\mathrm{EM}\sim T^{-b}$ does not adequately capture the character of the hot part of $\mathrm{EM}(T)$ over any reasonable temperature range. \citet{antiochos_evaporative_1978} showed analytically that accounting for evaporative cooling and assuming constant pressure gives $b=11/2$, though this value can be as low as $b=5/2$ if a flux limiter is included. However, in \citetalias{barnes_inference_2016}, we showed that in the case of a single 200 s nanoflare that heats only the electrons, the assumption of constant electron pressure during the heating and early conductive cooling phases does not hold. Our results here are consistent with our findings in \citetalias{barnes_inference_2016} in that the parameter $b$ does not provide any valuable information about $\mathrm{EM}(T)$ for $T>T_m$ when two-fluid effects are considered. Clearly, an alternative metric for measuring the amount of hot plasma in the emission measure distribution is needed. 

@@

		\plottwo{figures/ratio_hist_alpha_single_T1.pdf}{figures/ratio_hist_twait_single_T1.pdf}
		\caption{Histograms of emission measure ratios $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$, where $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.2}$ K, for all heating function types and heating frequencies for the single fluid case. In both panels each histogram is normalized such that for each distribution $P(x)$, $\int_{-\infty}^{\infty}\mathrm{d}x~P(x)=1$ and the bin widths are calculated using the Bayesian blocks method of \citet{scargle_studies_2013} as implemented in the astroML Python package for statistical learning in astronomy \citep{vanderplas_introduction_2012}. \textbf{Left:} Emission measure ratios separated by heating function type for all heating frequencies, $250\le t_N\le5000$ s. Because there are too few ($<20$) $\mathrm{EM}$ ratio measurements for the uniform case to construct a meaningful histogram, we denote the median of the uniform results with a vertical line, shown here in purple. \textbf{Right:} Emission measure ratios separated by waiting time, $t_N$. For aesthetic purposes, only five values of $t_N$ are shown, $t_N=1000,2000,3000,4000,5000$ s.}

@@

		\plottwo{figures/ratio_hist_alpha_electron_T1.pdf}{figures/ratio_hist_twait_electron_T1.pdf}

@@

		\plottwo{figures/ratio_hist_alpha_ion_T1.pdf}{figures/ratio_hist_twait_ion_T1.pdf}

@@

	\par One characteristic of the $\mathrm{EM}(T)$ distribution arising from low- and intermediate-frequency nanoflares is that $\mathrm{EM}(T)$ is dual-valued as a function of temperature \citep[see \autoref{fig:single_em}-\autoref{fig:ion_em} and][]{cargill_implications_1994}. For example, in the lower right panel of \autoref{fig:single_em}, $\mathrm{EM}\approx 10^{26.5}$ cm$^{-5}$ at $T = 10^{6.2}$ K and $10^{6.9}$ K. Given two observed temperatures (due say to specific emission lines), this suggests that predictions from the ratio of emission at these temperatures can be compared with data. This is of particular use where very limited spectral coverage is available either above or below $T_m$. Indeed for impulsive heating of any kind, the generic $\mathrm{EM}(T)$ curve remains similar (though not identical) as the magnitude of the heating changes. For flare-like energy release one would expect the hot emission to be much greater than the cold emission, with the opposite in the quiet Sun. For nanoflares, one might expect them to be of the same order.

@@

	\authorcomment1{Is this section really even necessary? Can the discussion be entirely contained in (last part of) the Results section? Or we could convert \autoref{subsec:diagnostics} to the Discussion section...}
